Significant wind disturbances induced by giant dunes.

### 2021-12-21 Paper/main.tex
Modifying all figures -- introducing day and night + color scheme across figures

  \begin{figure}
    \centering
    \includegraphics[scale=1]{Figures/Figure2.pdf}
    \caption{Temporal comparison between the wind data coming from the Era5Land climate reanalysis (orange lines) and from the local measurements (blue lines). \textbf{a--b}: Huab station. \textbf{c--d}: Deep Sea station in winter. \textbf{e--f}: Deep Sea station in summer.}
    \label{Fig2}
  \end{figure}

@@

  \begin{figure}
    \centering
    \includegraphics[scale=1]{Figures/Figure3.pdf}
    \caption{Distributions of wind direction at the Deep Sea Station for the Era5Land climate reanalysis (orange) and the local measurements (blue). In each subplot, both distributions are plotted from the same time steps, selected with constraints on the wind direction (columns) and/or wind velocity (rows) of the Era5Land dataset. The gray vertical dashed lines indicate the dune orientation, and the top right numbers the percentage of the total number of time steps selected in each subplot. The purple frame highlights the regime (small wind velocities, nocturnal summer wind) in which the data from both datasets differs. A similar figure can be obtained for the Deep Sea station (see Fig.~\ref{Fig6_supp}).}
    \label{Fig3}
  \end{figure}

@@

  \begin{figure}
    \centering
    \includegraphics[scale=1]{Figures/Figure4.pdf}
    \caption{\textbf{a--b}: Vertical profiles of the virtual potential temperature at 2 different time steps (blue - 29/11/2012 - 1100 UTC, red - 21/03/2017 - 1200 UTC) at the Deep Sea station. Dots: data from the ERA5 reanalysis. Transparent dashed lines: boundary layer height given by the ERA5 reanalysis, calculated from the bulk Richardson number \citep{seidel2012}. Plain lines: vertical (boundary layer) and linear (free atmosphere) fits to estimate the stratification properties. \textbf{c--f}: Sketches representing the interaction between the giant dunes and the atmospheric flow for different meteorological conditions. \textbf{g}: Streamlines qualitatively representing the effect of flow confinement, in the case of the Deep Sea station. The red lines are calculated from the unconfined case similar to \textbf{d}. The sinuous blue line represents a confined case similar to \textbf{f}. For details on the streamline derivation, see Appendix~\ref{turbulent_wind_model}.}
    %
    %
    % calculated from equation~\eqref{Tau}. Note that topography and wind geometry represent the case of the Deep Sea station. For the red and straight blue lines, $(\mathcal{A}_{0}, \mathcal{B}_{0}) = (3.8, 1.3)$, calculated from the unbounded case of \citep{Fourriere2010}, and representing the situations \textbf{b--c}. For the sinuous blue line, $(\mathcal{A}_{0}, \mathcal{B}_{0}) = (8, 2)$, representing the confined case of \textbf{d}.}
    \label{Fig4}
  \end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=1]{Figures/Figure6_supp.pdf}
  \caption{Distributions of wind direction at the South Namib Station for the Era5Land climate reanalysis (orange) and the in situ measurements (blue). In each subplot, both distributions are plotted from the same time steps, selected with constraints on the wind direction (columns) and/or wind velocity (rows) in the Era5Land dataset. The grey dashed vertical lines indicate the dune orientation. The purple frame highlights the regime (small wind velocities, nocturnal summer wind) during which the wind data from both datasets differs. A similar figure can be obtained for the South Namib station (see Fig.~\ref{Fig3}).}
  \label{Fig6_supp}
\end{figure}

>>>>

  \begin{figure}
    \centering
    \includegraphics[scale=1]{Figures/Figure2.pdf}
    \caption{Temporal comparison between the wind data coming from the Era5Land climate reanalysis (orange lines) and from the local measurements (blue lines). Color swathes indicate day (between 1000 UTC and 2200 UTC) and night (before 1000 UTC or after 2200 UTC) \textbf{a--b}: Huab station. \textbf{c--d}: Deep Sea station in winter. \textbf{e--f}: Deep Sea station in summer.}
    \label{Fig2}
  \end{figure}

@@

  \begin{figure}
    \centering
    \includegraphics[scale=1]{Figures/Figure3.pdf}
    \caption{Distributions of wind direction at the Deep Sea Station for the Era5Land climate reanalysis (orange) and the local measurements (blue). In each subplot, both distributions are plotted from the same time steps, selected with constraints on the wind direction (columns) and/or wind velocity (rows) of the Era5Land dataset. The gray vertical dashed lines indicate the dune orientation. The numbers at the top right give the percentage of time steps selected in each sub-range, as well as the percentage of them corresponding to the day (between 1000 UTC and 2200 UTC). The purple frame highlights the regime (small wind velocities, nocturnal summer wind) in which the data from both datasets differs. A similar figure can be obtained for the Deep Sea station (see Fig.~\ref{Fig6_supp}).}
    \label{Fig3}
  \end{figure}

@@

  \begin{figure}
    \centering
    \includegraphics[scale=1]{Figures/Figure4.pdf}
    \caption{\textbf{a--b}: Vertical profiles of the virtual potential temperature at 2 different time steps (blue - 29/11/2012 - 1100 UTC, red - 21/03/2017 - 1200 UTC) at the Deep Sea station. Dots: data from the ERA5 reanalysis. Transparent dashed lines: boundary layer height given by the ERA5 reanalysis, calculated from the bulk Richardson number \citep{seidel2012}. Plain lines: vertical (boundary layer) and linear (free atmosphere) fits to estimate the stratification properties. \textbf{c--f}: Sketches representing the interaction between the giant dunes and the atmospheric flow for different meteorological conditions. \textbf{g}: Streamlines qualitatively representing the effect of low, medium and high flow confinement. For details on the streamline derivation, see Appendix~\ref{turbulent_wind_model}.}
    \label{Fig4}
  \end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[scale=1]{Figures/Figure6_supp.pdf}
  \caption{Distributions of wind direction at the South Namib Station for the Era5Land climate reanalysis (orange) and the in situ measurements (blue). In each subplot, both distributions are plotted from the same time steps, selected with constraints on the wind direction (columns) and/or wind velocity (rows) in the Era5Land dataset. The gray vertical dashed lines indicate the dune orientation. The numbers at the top center give the percentage of time steps selected in each sub-range, as well as the percentage of them corresponding to the day (between 1000 UTC and 2200 UTC). The purple frame highlights the regime (small wind velocities, nocturnal summer wind) during which the wind data from both datasets differs. A similar figure can be obtained for the South Namib station (see Fig.~\ref{Fig3}).}
  \label{Fig6_supp}
\end{figure}
